Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Simplified explanation of rendering part behind intersection in first approach

Next the volumes behind the intersection are rendered into the results texture.
Because we want the part of the volume behind the intersection we first render
the texture coordinates of the back faces of the cubes into a framebuffer, then
render the back faces of the intersection as per \cite{Kruger03}.  Note in the code
snippet below we only show the first volume, hide where we set the uniform
variables in the shader program for brevity, and give the intersection an ID so
it can be redrawn later.

>>>>

Next the part of the volume behind the intersection is rendered into the results
texture.  To get just that part the back faces of the Boolean AND are used
instead of the front faces of the cube.  Note in the code snippet below we only
show the first volume, hide where we set the uniform variables in the shader
program for brevity, and give the intersection an ID so it can be redrawn later.
